A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-16 paper.tex
Clarify the privacy concerns

Our work has a main focus on the subscription-based model and relative experiments. And the next step is extending it to:
\begin{enumerate}
	\item reduce the use of Gas in key-agreement protocol and consider the possibility of the zero-knowledge proof to lower transaction costs;
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}

>>>>

Our work has a main focus on the subscription-based model and relative experiments. And the next step is extending it to:
\begin{enumerate}
	\item reduce the use of Gas in key-agreement protocol and consider the possibility of the zero-knowledge proof to lower transaction costs;
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality, without violating the privacy.
\end{enumerate}
